model

### 2022-08-01 analysis/gafo-cc-model-hier.Rmd
update from server

```{r, message=FALSE, warning=F}
model <- rbindlist(
  list(
     fread("../model/output/gafo-cc-hier_gran_20_chain1.csv"),
     fread("../model/output/gafo-cc-hier_gran_20_chain2.csv"),
     fread("../model/output/gafo-cc-hier_gran_20_chain3.csv")
    ), use.names=TRUE)#%>%saveRDS("../models/output/model_kids_box.rds")

# saveRDS(model, "../model/output/gafo-cc-model.rds")
# 
# model <- readRDS("../model/output/gafo-cc-model.rds")
```

@@

```{r}
model%>%
  filter(scope == "global", 
         parameter == "guessing")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type, scales = "free_y")+
  theme_few()+
  scale_fill_viridis_d()
```

@@

```{r}
model%>%
  filter(scope == "global", 
         parameter == "inference")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(~type, scales = "free_y")+
  theme_minimal()+
  scale_fill_viridis_d()
```

@@

```{r}
model%>%
  filter(scope == "community", 
         parameter == "guessing")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type, scales = "free_y")+
  theme_few()+
  scale_fill_viridis_d()
```

@@

```{r}
model%>%
  filter(scope == "community", 
         parameter == "bias")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type)+
  theme_few()+
  scale_fill_viridis_d()
```

@@

```{r}
guess_map <- model%>%
  filter(scope == "global", 
         parameter == "guessing")%>%
  group_by(community, type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(guess = plogis(intercept + slope * age))

guess_samp <- model%>%
  filter(scope == "global",
         parameter == "guessing")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  #sample_n(1000)%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(guess = plogis(intercept + slope * age))

@@

#### Bias
```{r}
bias_map <- model%>%
  filter(scope == "global", 
         parameter == "bias")%>%
  group_by(community,type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(bias = plogis(intercept + slope * age))

bias_samp <- model%>%
  filter(scope == "global",
         parameter == "bias")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  #sample_n(1000)%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(bias = plogis(intercept + slope * age))

@@

```{r}
inf_map <- model%>%
  filter(scope == "global", 
         parameter == "inference")%>%
  group_by(community,type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(sd_inf = plogis(intercept + slope * age))

inf_samp <- model%>%
  filter(scope == "global",
         parameter == "inference")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  group_by(chain)%>%
  #sample_n(1000)%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(sd_inf = plogis(intercept + slope * age))

>>>>

```{r, message=FALSE, warning=F}
model <- rbindlist(
  list(
     fread("../model/output/gafo-cc-hier_gran_20_chain1.csv"),
     fread("../model/output/gafo-cc-hier_gran_20_chain2.csv"),
     fread("../model/output/gafo-cc-hier_gran_20_chain3.csv"),
     fread("../model/output/gafo-cc-hier_gran_20_chain4.csv"),
     fread("../model/output/gafo-cc-hier_gran_20_chain5.csv")
    ), use.names=TRUE)#%>%saveRDS("../models/output/model_kids_box.rds")

#saveRDS(model, "../model/output/gafo-cc-model_hier.rds")
# 
# model <- readRDS("../model/output/gafo-cc-model.rds")
```

@@

```{r}
model%>%
  filter(scope == "global", 
         parameter == "guessing",
         chain != 1)%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type, scales = "free_y")+
  theme_few()+
  scale_fill_viridis_d()
```

@@

```{r}
model%>%
  filter(scope == "global", 
         parameter == "inference",
         chain != 1)%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(~type, scales = "free_y")+
  theme_minimal()+
  scale_fill_viridis_d()
```

@@

```{r}
model%>%
  filter(scope == "community", 
         parameter == "guessing",
         chain != 1)%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type, scales = "free_y")+
  theme_few()+
  scale_fill_viridis_d()
```

@@

```{r}
model%>%
  filter(scope == "community", 
         parameter == "bias",
         chain != 1)%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type)+
  theme_few()+
  scale_fill_viridis_d()
```

@@

```{r}
guess_map <- model%>%
  filter(scope == "community", 
         parameter == "guessing")%>%
  group_by(community, type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(guess = plogis(intercept + slope * age))

guess_samp <- model%>%
  filter(scope == "community",
         parameter == "guessing")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  sample_n(1000)%>%
  group_by(community)%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(guess = plogis(intercept + slope * age))

@@

#### Bias
```{r}
bias_map <- model%>%
  filter(scope == "community", 
         parameter == "bias")%>%
  group_by(community,type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(bias = plogis(intercept + slope * age))

bias_samp <- model%>%
  filter(scope == "community",
         parameter == "bias")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  sample_n(1000)%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(bias = plogis(intercept + slope * age))

@@

```{r}
inf_map <- model%>%
  filter(scope == "community", 
         parameter == "inference")%>%
  group_by(community,type)%>%
  summarise(mode = estimate_mode(value))%>%
  pivot_wider(names_from = "type", values_from = "mode")%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(sd_inf = plogis(intercept + slope * age))

inf_samp <- model%>%
  filter(scope == "community",
         parameter == "inference")%>%
  pivot_wider(names_from = "type", values_from = "value")%>%
  group_by(chain)%>%
  sample_n(1000)%>%
  expand_grid(age = seq(0,5.5, by = 0.1))%>%
  mutate(sd_inf = plogis(intercept + slope * age))

### 2022-08-01 analysis/gafo-cc-model.Rmd
update from server

```{r}
model%>%
  filter(scope == "global", 
         parameter == "guessing")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(community~type, scales = "free_y", nrow = 2)+
  theme_few()+
  scale_fill_viridis_d()
```

@@

```{r}
model%>%
  filter(
         parameter == "bias")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type)+
  theme_few()+
  scale_fill_viridis_d()
```

@@

```{r}
model%>%
  filter(scope == "global", 
         parameter == "inference")%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(~type, scales = "free_y")+
  theme_minimal()+
  scale_fill_viridis_d()
```
## Development

@@

```{r}
alt <- model%>%
  filter(scope == "global", 
         parameter != "inference",
         chain != 7,
         chain != 2)%>%
  group_by(community,parameter,type)%>%
  summarise(mode = estimate_mode(value))%>%
  filter(type != "sigma")%>%
  pivot_wider(names_from = c("parameter", "type"), values_from = "mode")%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(guess = plogis(guessing_intercept + guessing_slope * age),
         bias_raw = plogis(bias_intercept + bias_slope * age),
         inference = 1- guess,
         center_bias = guess * bias_raw,
         random_guessing = 1- inference - center_bias)%>%
  ungroup()%>%
  select(age,community, center_bias, random_guessing, inference)%>%
  pivot_longer(names_to = "parameter", values_to = "value", cols = c(center_bias, random_guessing, inference))%>%
  mutate(parameter = factor(parameter, levels = c("inference", "random_guessing", "center_bias")))

>>>>

```{r}
model%>%
  filter(scope == "global", 
         parameter == "guessing",
         chain != 5,
         chain != 6)%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(community~type, scales = "free_y", nrow = 2)+
  theme_few()+
  scale_fill_viridis_d()
```

@@

```{r}
model%>%
  filter(
         parameter == "bias",
         chain != 5)%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_grid(community~type)+
  theme_few()+
  scale_fill_viridis_d()
```

@@

```{r}
model%>%
  filter(scope == "global", 
         parameter == "inference",
         chain != 5,
         chain != 4)%>%
ggplot(aes(x= value, fill = factor(chain)))+
  geom_density(alpha = .5)+
  facet_wrap(community~type, scales = "free_y")+
  theme_minimal()+
  scale_fill_viridis_d()
```
## Development

@@

```{r}
alt <- model%>%
  filter(scope == "global", 
         parameter != "inference")%>%
  group_by(community,parameter,type)%>%
  summarise(mode = estimate_mode(value))%>%
  filter(type != "sigma")%>%
  pivot_wider(names_from = c("parameter", "type"), values_from = "mode")%>%
  expand_grid(age = seq(0,3, by = 0.1))%>%
  mutate(guess = plogis(guessing_intercept + guessing_slope * age),
         bias_raw = plogis(bias_intercept + bias_slope * age),
         inference = 1- guess,
         center_bias = guess * bias_raw,
         random_guessing = 1- inference - center_bias)%>%
  ungroup()%>%
  select(age,community, center_bias, random_guessing, inference)%>%
  pivot_longer(names_to = "parameter", values_to = "value", cols = c(center_bias, random_guessing, inference))%>%
  mutate(parameter = factor(parameter, levels = c("inference", "random_guessing", "center_bias")))
